Methods for Large Scale Learning to Rank

### 2014-03-12 report/Chapters/RelatedWork.tex
5e forward search resultaat verwerkt

Lee and Lin \cite{Lee2014} describe a lower time complexity method to train a linear kernel RankSVM \cite{Herbrich1999, Joachims2002}. The authors observed that linear kernel RankSVMs are inferior in accuracy compared to nonlinear kernel RankSVMs and \ac{GBDT}s and are mainly useful to quickly produce a baseline model. Details of the lower time complexity version of the linear kernel RankSVM will not be discussed as it is shown to be an inferior Learning-to-Rank method in terms of accuracy.\\

>>>>

Airola et al. \cite{Airola2011} and Lee and Lin \cite{Lee2014} have both described lower time complexity methods to train a linear kernel RankSVM \cite{Herbrich1999, Joachims2002}. Lee and Lin \cite{Lee2014} observed that linear kernel RankSVMs are inferior in accuracy compared to nonlinear kernel RankSVMs and \ac{GBDT}s and are mainly useful to quickly produce a baseline model. Details of the lower time complexity version of the linear kernel RankSVM will not be discussed as it is shown to be an inferior Learning-to-Rank method in terms of accuracy.\\
